---
title: "Introduction to paratests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paratests-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(paratests)
```

This is the introduction to my DSFB2 portfolio R package paratests. It is used to depict descriptive graphs and perform parametric, statistical tests. 

Here we will show an example of how functions can be used together to analyze the PlantGrowth data set.

```{r}
# Load data:
PlantGrowth <- readRDS(here::here("data_raw", "03_plantgrowth", "PlantGrowth.rds"))

# Use the gem_barchart function to visualize the mean and standard deviation of weight per condition
gem_barchart(PlantGrowth, group, weight)

# perform a Shapiro Wilk on the weight values per condition to check for normality (a parametrical test requires every group to be normally distributed):
sw_tidy(PlantGrowth, group, weight)
```

The three obtained P-values are above 0.05, which means the three experimental groups are normally distributed. We get green light to perform an ANOVA.

```{r}
anova(PlantGrowth$weight, PlantGrowth$group)
```


The obtained P-value is under 0.05, which means there is a statistical significant difference in weight amoung the three experimental groups.

Let's add some fake data about the height of the measured plants to demonstrate the cor_scatterplot function.

```{r}
PlantGrowth <- PlantGrowth %>% mutate(height = abs(rnorm(30, 10, 2)), .after = 1)

cor_scatterplot(PlantGrowth, PlantGrowth$weight, PlantGrowth$height, PlantGrowth$group, reposition_r = 1) # Use the reposition_r argument to adjust the "Pearson's r = #" label position on the x axis. The default is set as 'lowest x axis value + 10'.
```

Since Pearson's r correlation coefficient is below 0.99 and the P-value for this correlation is above 0.05, there doesn't seem to be a (statistical significant) correlation between plant weight and the randomly generated plant heights.
