---
title: "Introduction to paratests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paratests-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(paratests)
library(dplyr)
library(ggplot2)
```

This is the introduction to my R package {paratests}. It is used to depict descriptive graphs and perform parametric, statistical tests as well as non-parametric tests. 

Here we will show an example of how {paratests} functions can be used together to analyze the PlantGrowth data set.

```{r}
# Load data:
data("PlantGrowth_edit")

# Use the mean_barchart function to visualize the mean and standard deviation of weight per condition
mean_barchart(PlantGrowth_edit, group, weight)

# perform a Shapiro Wilk on the weight values per condition to check for normality (a parametrical test requires every group to be normally distributed):
sw_tidy(PlantGrowth_edit, group, weight)
```

The three obtained P-values are above 0.05, which means the three experimental groups are normally distributed. We get green light to perform an ANOVA.

```{r}
anova(PlantGrowth_edit$weight, PlantGrowth_edit$group)
```


The obtained P-value is under 0.05, which means there is a statistical significant difference in weight amoung the three experimental groups.

I added some fake data about the height and amount of leafs of the measured plants to demonstrate the cor_scatterplot function. The correlation scatterplot should show that a heigher plant has more leafs.

```{r}
cor_scatterplot(PlantGrowth_edit, PlantGrowth_edit$height, PlantGrowth_edit$leafs, PlantGrowth$group, reposition_r = 4) # Use the reposition_r argument to adjust the "Pearson's r = #" label position on the x axis. The default is set as 'lowest x axis value + 10'.
```

Since Pearson's r correlation coefficient is 0.99 and the P-value for this correlation is below 0.05, there seems to be a statistical significant correlation between plant height and the number of leafs for each group.
